\documentclass{article}
\begin{document}
\title{Cloud Associate Engineer Amazon Interview Questions}
\maketitle
\begin{itemize}
	\item If a server failed to do a nightly backup, what could be a reason for that?
	\item What is the difference between Bandwidth, Delay, and Latency?
	\item What is MTU, Window Size, Segment (MSS)?
	\item Describe 3-way handshake
	\item How does DNS work?
	\item How does DHCP work?
	\item What is BGP and describe the states - Idle, Connect, Active, Opensent, Openconfirm, Established.
	\item What is EIGRP?
	\item Scenario question about Stateful/Stateless firewall
	\item Scenario question about prefix-match and route summarization
	\item Scenario question about packet flow in NAT
	\item What is Active Directory and why would anyone use it?
	\item What is the importance of time in a windows domain?
	\item What is sysprep, sysvol, BSoD, DHCP, DNS, DFSR, WINS, Global Catalog
	\item Describe built-in tools to troubleshoot network issues.
	\item What are some best security practices and a scenario on a company under DOS attack and you choose best answers or suggest any additional answer - Quiz.
	\item Build a system that is robust and fault-tolerence for a start-up ecommerce website.
	\item What do you know about Hypervisor, VMWare, Windows Troubleshooting.
	\item What will you do when you type a website and website isn't loading up? How do you troubleshoot?
	\item What do you know about Active directories in Windows Server?
	\item How would you handle a customer who complains that all his data has been lost and has no backup?
	\item How do you design your web application on AWS?
	\item Difference between cloud and traditional services, what would you improve in AWS?
	\item What is the difference between range and xrange is python?
	\item How would you troubleshoot if ssh is not working?
	\item What commands will you use to find the disk space?
	\item HTTP Codes? - https://httpstatuses.com
	\item How to troubleshoot a slow computer?
	\item How to deal with a data loss complain from a client?
	\item What and how the load value is calculated which is displayed when you give the command "uptime"?
	\item Linux server troubleshooting steps?
	\item Explain IPSec briefly.
	\item What are the steps to resolving www.amazon.com
	\item What is TCP?
	\item What is UDP? Differences between UDP and TCP, what kind of application base on UDP?
	\item What protocol is used and how to gate out from private network. (ARP)?
	\item Why Amazon?
	\item Explain DNS System.
	\item What if you have two customers with same problem at the same time, whom you will give the priority and why?
	\item What are the problems you found with AWS?
	\item Difference between RAID2 and RAID5, mdadm?
	\item A client in Germany is trying to access a server in London, but his connection is running slow. You are in Dublin. How do you diagnose the issue?
	\item What happens when you press the power button on your PC?
	\item I have forgotten my password, how will you help me?
	\item How do you find out your IP Address is?
	\item What is FTP? What kind of application it used for?
	\item What is the difference between HTTP and HTTPS? and why HTTPS is more secure?
	\item Difference between DNS and IP?
	\item Difference between Private IP and Public IP?
	\item Difference between Cloud and Virtualization?
	\item How to handle problems like CPU is 100\% occupied or the computer is slow. What are the possible problems?
	
\end{itemize}
\end{document}