\documentclass{article}
\begin{document}
\title{Apple Software Engineer Interview Questions}
\maketitle
\begin{itemize}
	\item Implement a peek using a existing iterator next and has-next function.
	\item What is the difference between weak and strong pointers
	\item Reverse a linked list recursively
	\item Why can't you use primitives in a hash-map.
	\item Traverse a binary tree recursively.
	\item Write a basic Fibonacci sequence implementation. 
	\item How does delegation work?
	\item How does ARC work in Objective C, and how is it different from garbage collection?
	\item How would you design a data structure that is an array, but with so many elements such that the array almost fills up the entire RAM?
	\item How would you reverse a singly-linked list?
	\item What is the run time of a binary search tree.
	\item Find the most frequent element in an integer array.
	\item Is Java pass by value or pass by reference?
	\item What data structure would you use to auto complete a dialer when the phone may have thousands or hundreds of thousands of entries.
	\item Find the K th largest number in an array.
	\item What is deadlock and how is it prevented? Intersection of two arrays with optimal Big O.
	\item What is the instruction used in Matlab to compute the standard deviation?
	\item Write a simple C++ algorithm involving standard input and output. Provide test cases.
	\item How do you design a system for detecting people around a door, predict whether this man will go into the door.
	\item Skyline problem.
	\item Given a set of interval tuples, find the longest overlapping interval.
	\item Given a huge log file of a web server, find the IP addresses that had exactly 1 request.
	\item A network is connected in a line, so that servers can talk only to the servers to their left or right. Servers know if they are the leftmost or rightmost servers. What's a protocol for every server to learn the full topology? How long does it take?
	\item Implement a queue using array or linked-list.
	\item What is polymorphism?
	\item How could you approximate a non-linear function with only multiplication and additions. 
	\item What are the techniques for allocating static and dynamic memory.
	\item Find the first non-repeated element in C.
	\item Given a binary search tree, print the nodes at each level on a separate line. With O (n) time complexity and O(1) space complexity.
	\item Describe the process of an interaction on a web page button from the click to the response.
	\item What is NTP and explain how TCP works?
	\item Given an iTunes type of an application that pulls down lots of images that get stale over time, what strategy would you use to flush disused images over time?
	\item Is there a difference between performSelector and a performSelector with delay of 0?
	\item Write a function to reverse a string.
	\item If you have 2 eggs, and you want to figure out what's the highest floor from which you can drop the egg without breaking it, how would you do it? What's the optimal solution?
	\item What is polymorphism?
	\item What does final keyword do in Java?
	\item How would you go through a list of country music words?
	\item Write code to find out the frequency of common words.
	\item Given a deck of cards, write a method to determine if it is "flush".
	\item Given busy slots as a data-set in a person's calendar (ex: {(1000,1200),(1415,1530),..}) and the time required for a meeting (ex: 45 minutes). Write a method to find an open available slot for scheduling a meeting.
	\item Assume you have many pages of slides, you want to change the order when you are editing them, say, you would like to insert the 7th page after the 3rd page and before the 4th page. Design and implement your idea.
	\item Find the smallest number in an array
	\item Find duplicate words in a file implementing uniq.
	\item What are the run levels of init.
	\item There is a mission critical (i.e., cannot to be rebooted) server that is lagging hard. You only have a terminal/shell prompt. How do you debug it?
	\item Reverse a string in Python without using str.reverse()
	\item Write code in Objective-C to return the first repeated integer from a given array, with O(n) time.
	\item How would you speed up your typical bit reversal algorithm?
	\item How large file can be on HDFS distributed file system?
	\item Given an integer, write code to list all primes preceding it.
	\item Explain singleton class in Java
	\item Given an array with N-2 elements (two missing) from 1 to N, find the two missing elements in linear time and constant memory usage.
	\item How would you design evernote app.
	\item Find circular loop in linked list.
	\item Ants are at the corners of an equilateral triangle labeled 1, 2, and 3, each ant starts moving towards the next one (1 towards 2, 2 towards 3, 3 towards 1) at the same constant speed. How long until they meet?
	\item How to speed up a database query?
	\item Implement strstr using a linked list of linked lists.
	\item Create a synchronization primitive for the operating system/kernel from scratch.
	\item Create a primitive that doesn't waste CPU cycles. (essentially, how would you create a mutex inside the kernel?)
	\item Collapse a binary search tree into a sorted list.
	\item What is the difference between Grand Central Dispatch, NSThread, and NSOperation and when would you use each?
	\item Implement an iterator for a binary search tree that will iterate the nodes by value in ascending order.
	\item Explain semaphores.
	\item Difference between thread and a process.
	\item What is the difference between 64 vs 32 bit addressing.
	\item Model an elevator.
	\item Why do you write "assign" in a property declaration on an Objective-C class.
	\item Reverse a C string that has a special character encoding.Special characters are two bytes and are preceded by a flag character represented by the highest bit being set to 1, then the following bits specifying how many special characters will follow. The special characters are be interspersed between normal characters.  	
\end{itemize}
\end{document}