\documentclass{article}
\begin{document}
\title{Microsoft Software Engineer Interview Questions}
\maketitle
\begin{itemize}
	\item Traverse a binary tree using recursion.
	\item How will you find the height of a binary tree? Write a function to find the height.
	\item Explain how you will reverse a singly linked list. 
	\item You have two intersecting linked lists. Describe a function that returns a pointer to the node where they intersect.
	\item Find the first 1 entry in an array of binary numbers.
	\item Design a function to merge a list of contacts between various clients updating a web service.
	\item Create an algorithm to place a series of randomized ships onto a battleship (game) -esque grid system.
	\item Create an algorithm to determine whether pixels surrounding a grid spot in a game of life environment are turned on.
	\item Write the shunting yard algorithm without a stack.
	\item How would you design a fridge for blind?
	\item How would you do an in order traverse of a tree without recursion.
	\item Divide two numbers without using / or \% and return quotient.
	\item Are two words palindrome of each other?
	\item Given a list of numbers, sort them and remove the duplicate numbers.
	\item You have two substrings of a string that overlap. How would you put them together into one string?
	\item Write an atoi function.
	\item Given two sorted arrays, combine the two arrays in order without using a sort algorithms after the merge?
	\item Remove duplicates from a linked list.
	\item Given a string of digits like "46278" and int n, delete n characters from the string such that the resultant string contains minimal number representation, you must preserve relative position of digits. Example: if the string = "72388" and n=2, the output should be 238.
	\item Write an algorithm to parse string for algebraic operations and solve with respect to order.
	\item Remove duplicates from a string.
	
\end{itemize}
\end{document}